SMT-Based Context-Bounded Model Checking for Embedded Systems: Challenges and Future Trends

### 2016-03-26 paper.tex
corrections to section 4

This position paper tackles four major problems in computer-aided verification for embedded systems, which are (partially) open in present research.

\textbf{(RP1)} provide suitable encoding into the Satisfiability Modulo Theories (SMT) \cite{BarrettSST09}, which may extend the background theories typically supported by SMT solvers, with the goal of reasoning accurately and effectively about realistic embedded programs.

>>>>

This position paper tackles four major problems in computer-aided verification for embedded systems, which are (partially) open in current published research.

\textbf{(RP1)} provide suitable encoding into SMT \cite{BarrettSST09}, which may extend the background theories typically supported by SMT solvers, with the goal of reasoning accurately and effectively about realistic embedded programs.
